Neural Textures make Better Simulators ``I can't believe it's not real!"

### 2022-06-12 CORL/example.tex
Commented out incomplete introduction

TODO: Note that the simple input of UVL, or an RGB neural texture, means any simulator should be plug-and-play with this algorithm.

Recently, several sim-to-real algorithms have come out that are based on image-to-image translation. [Citations]
These are used for training robots using pixel-based reinforcement learning.
They demonstrated that better image translation algorithms yielded notable improvements in robotic benchmarks.
At the same time, there is a lot of research on differentiable rendering,
a topic which produced papers such as NERF which attempt to capture 3d representations of the real world.
However, most of these approaches are either supervised or involve only camera movements [citations].
One paper that came out recently combined both image translation and differentiable rendering in an unsupervised manner to create view-consistent models of human organs [citation].
This paper too, though, was limited to only camera movements.

This algorithm unlocks a new capability: learning textures to match photos for given 3d models without supervision.

The motivation for this paper is to create a temporally consistent sim-to-real image translation algorithm that will look the same from multiple camera angles simultaneously, keeps all semantic details 
[[I'll finish this later... let's work on the meat of the paper first...]]

@@

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=270pt]{../images/uvl_explanation_minimal.pdf}
	\end{center}
	\caption{
		% This diagram shows the purpose of a UVL image.
		A UVL scene is an image that has three channels: RGB.
		R and G are used for U and V, and B is used for L.
		L stands for Label, and determines which part of the synthetic image will get which texture.
		The U and V coordinates correspond to positions on each texture,
		telling it how to project the textures onto the 3d objects represented in the UVL scene.
		The darkest shade of blue corresponds to the 1st texture, and the next darkest shade of blue corresponds to the 2nd texture etc.
		}
	\label{fig:uvl_explanation}
\end{figure}

@@

\subsection*{Data}

>>>>

I introduce you to TRITON. The rest of the introduction text goes here; I've commented out my old incomplete introduction.

% TODO: Note that the simple input of UVL, or an RGB neural texture, means any simulator should be plug-and-play with this algorithm.

% Recently, several sim-to-real algorithms have come out that are based on image-to-image translation. [Citations]
% These are used for training robots using pixel-based reinforcement learning.
% They demonstrated that better image translation algorithms yielded notable improvements in robotic benchmarks.
% At the same time, there is a lot of research on differentiable rendering,
% a topic which produced papers such as NERF which attempt to capture 3d representations of the real world.
% However, most of these approaches are either supervised or involve only camera movements [citations].
% One paper that came out recently combined both image translation and differentiable rendering in an unsupervised manner to create view-consistent models of human organs [citation].
% This paper too, though, was limited to only camera movements.

% This algorithm unlocks a new capability: learning textures to match photos for given 3d models without supervision.

% The motivation for this paper is to create a temporally consistent sim-to-real image translation algorithm that will look the same from multiple camera angles simultaneously, keeps all semantic details 
% [[I'll finish this later... let's work on the meat of the paper first...]]

@@

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=400pt]{../images/uvl_explanation_minimal.pdf}
	\end{center}
	\caption{
		% This diagram shows the purpose of a UVL image.
		A UVL scene is an image that has three channels: RGB.
		R and G are used for U and V, and B is used for L.
		L stands for Label, and determines which part of the synthetic image will get which texture.
		The U and V coordinates correspond to positions on each texture,
		telling it how to project the textures onto the 3d objects represented in the UVL scene.
		The darkest shade of blue corresponds to the 1st texture, and the next darkest shade of blue corresponds to the 2nd texture etc.
		}
	\label{fig:uvl_explanation}
\end{figure}

@@

\subsection{Data}
